---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height=4,
  out.width = "100%"
)
```
# xrayspecs

<!-- badges: start -->
<!-- badges: end -->

The goal of xrayspecs is to display model-agnostic iterpretations of black-box models.

## Installation

You cannot currently install xrayspecs from [CRAN](https://CRAN.R-project.org). However, you can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mt-edwards/xrayspecs")
```
## Example

```{r setup}
library(xrayspecs)
```

### Data set

The `mtcars` data set is used for this example. The `dplyr` package is used to transform the categorical features (`cyl`, `vs`, `am`, `gear` and `carb`) to factors. These trasformations are required so that the `dependence_plot` function knows how to plot the feature predictions. For example, the predictions of continuous features are displayed with line plots and the predictions of categorical features are displayed with bar plots.

```{r message=FALSE, warning=FALSE}
library(dplyr)

mtcars <- mtcars %>% 
  mutate(
    cyl = factor(cyl),
    vs = factor(vs),
    am = factor(am),
    gear = factor(gear),
    carb = factor(carb)
  )
```

### Random forest and linear regression models

A [random forest](https://en.wikipedia.org/wiki/Random_forest) and a [linear regression](https://en.wikipedia.org/wiki/Linear_regression) model are fit to the `mtcars` data set using the `parsnip` package. The `parsnip` package provides a unified framework for fitting models in `R`. The models that are available for fitting in `parsnip` are listed [here](https://tidymodels.github.io/parsnip/articles/articles/Models.html). The `xrayspecs` package is designed to integrate into the `parsnip` package's unified framework.

```{r message=FALSE, warning=FALSE}
library(parsnip)

# Random forest
rf <- rand_forest(mode = "regression") %>% 
  set_engine("ranger") %>% 
  fit(mpg ~ ., data = mtcars)

# Linear regression
lr <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(mpg ~ ., data = mtcars)
```

### Permutation importance plot

To display a [permutation importance](https://christophm.github.io/interpretable-ml-book/feature-importance.html) plot of the random forest and linear regression features all you need to do is pipe the `rf` and `lr` objects into the `importance_plot` function along with the data set (`mtcars`). Multiple plots are displayed using the `cowplot` package.

```{r message=FALSE, warning=FALSE}
library(cowplot)

# Random forest
p1 <- rf %>% 
  importance_plot(mtcars) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  importance_plot(mtcars) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```

### Partial dependence plot

To display a [partial dependence](https://christophm.github.io/interpretable-ml-book/pdp.html) plot of a random forest feature all you need to do is pipe the `rf` object into the `dependence_plot` function along with the data set (`mtcars`) and the name of the feature. Here the the partial dependece plots of the most "important" continuous and categorical features (`wt` and `cyl`) are displayed.

```{r message=FALSE, warning=FALSE}
# Random forest
p1 <- rf %>% 
  dependence_plot(mtcars, wt) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  dependence_plot(mtcars, wt) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```

```{r}
# Random forest
p1 <- rf %>% 
  dependence_plot(mtcars, cyl) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  dependence_plot(mtcars, cyl) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```
