---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height=4,
  out.width = "100%"
)
```
# xrayspecs

<!-- badges: start -->
<!-- badges: end -->

The `xrayspecs` package provides model-agnostic interpretations of black-box models. The package is designed to integrate into the `parsnip` package's unified modelling framework.

## Installation

You cannot currently install xrayspecs from [CRAN](https://CRAN.R-project.org). However, you can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mt-edwards/xrayspecs")
```
## Example

```{r setup}
library(xrayspecs)
```

### Data Set

The `mtcars` data set is used for this example. The `dplyr` package is used to transform the categorical features (`cyl`, `vs`, `am`, `gear` and `carb`) to factors. These trasformations are required so that the `dependence_plot` function knows how to plot the feature predictions. For example, the predictions of continuous features are displayed with line plots and the predictions of categorical features are displayed with bar plots.

```{r message=FALSE, warning=FALSE}
library(dplyr)

mtcars <- mtcars %>% 
  mutate(
    cyl = factor(cyl),
    vs = factor(vs),
    am = factor(am),
    gear = factor(gear),
    carb = factor(carb)
  )
```

### Random Forest and Linear Regression Models

A [random forest](https://en.wikipedia.org/wiki/Random_forest) and a [linear regression](https://en.wikipedia.org/wiki/Linear_regression) model are fit to the `mtcars` data set using the `parsnip` package. The `parsnip` package provides a unified framework for fitting models in `R`. The models that are available for fitting in `parsnip` are listed [here](https://tidymodels.github.io/parsnip/articles/articles/Models.html). The `xrayspecs` package is designed to integrate into the `parsnip` package's unified framework.

```{r message=FALSE, warning=FALSE}
library(parsnip)

# Random forest
rf <- rand_forest(mode = "regression") %>% 
  set_engine("ranger") %>% 
  fit(mpg ~ ., data = mtcars)

# Linear regression
lr <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(mpg ~ ., data = mtcars)
```

### Permutation Importance Plot

To display a [permutation importance](https://christophm.github.io/interpretable-ml-book/feature-importance.html) plot of the random forest and linear regression features all you need to do is pipe the `rf` and `lr` objects into the `plot_importance` function along with the data (`mtcars`) the target (`mpg`) and a metric from the `yardstick` package, e.g. `mae` (Mean Absolute Error). Multiple plots are displayed using the `cowplot` package. A feature importance is equal to the absolute difference between the metric estimates when the feature is and is not permuted in the data. **Note**: metrics must be appropriate for the target variable.

```{r message=FALSE, warning=FALSE}
library(yardstick)
library(cowplot)

# Random forest
p1 <- rf %>% 
  plot_importance(mtcars, mpg, mae) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  plot_importance(mtcars, mpg, mae) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```

### Partial Dependence Plot

To display a [partial dependence](https://christophm.github.io/interpretable-ml-book/pdp.html) plot of a feature for the random forest and linear regression models all you need to do is pipe the `rf` and `lr` objects into the `dependence_plot` function along with the data (`mtcars`) and the feature. Here the partial dependence plots of the most "important" continuous and categorical features (`wt` and `cyl`) are displayed.

```{r message=FALSE, warning=FALSE}
# Random forest
p1 <- rf %>% 
  plot_dependence(mtcars, wt) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  plot_dependence(mtcars, wt) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```

```{r}
# Random forest
p1 <- rf %>% 
  plot_dependence(mtcars, cyl) +
  labs(subtitle = "Random Forest")

# Linear regression
p2 <- lr %>% 
  plot_dependence(mtcars, cyl) +
  labs(subtitle = "Linear Regression")

plot_grid(p1, p2)
```
