---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# xrayspecs

<!-- badges: start -->
<!-- badges: end -->

The goal of xrayspecs is to do model-agnostic iterpretation of black-box models.

## Installation

You cannot currently install xrayspecs from [CRAN](https://CRAN.R-project.org). However, you can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mt-edwards/xrayspecs")
```
## Example

```{r setup}
library(xrayspecs)
```

### Data set

The `mtcars` data set is used for this example. The `dplyr` package is used to transform the categorical features (`cyl`, `vs`, `am`, `gear` and `carb`) to factors. The trasformation is required so that the `effect_plot` function, from the `xrayspecs` package, knows how to plot the feature effects. For example, the effect of numeric features are displayed with line plots and the effect of factor features are displayed with bar plots.

```{r message=FALSE, warning=FALSE}
library(dplyr)

mtcars <- mtcars %>% 
  mutate(
    cyl = factor(cyl),
    vs = factor(vs),
    am = factor(am),
    gear = factor(gear),
    carb = factor(carb)
  )
```

### Random forest and linear regression models

A random forest and a linear regression model is fit to the `mtcars` data set using the `parsnip` package. The `parsnip` package provides a unified framework for fitting models in `R`. The models that are available for fitting in `parsnip` are listed [here](https://tidymodels.github.io/parsnip/articles/articles/Models.html). The `xrayspecs` package is designed to integrate into the `parsnip` package framework.

```{r message=FALSE, warning=FALSE}
library(parsnip)

# Random forest
rf <- rand_forest(mode = "regression") %>% 
  set_engine("ranger") %>% 
  fit(mpg ~ ., data = mtcars)

# Linear regression
lr <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(mpg ~ ., data = mtcars)
```

### Permutation importance plot

To display a permutation importance plot of the random forest and linear regression features all you need to do is pipe the `rf` and `lr` objects into the `importance_plot` function along with the data set (`mtcars`) and the name of the target variable (`mpg`). Multiple plots are displayed using the `cowplot` package.

```{r message=FALSE, warning=FALSE}
library(cowplot)

p1 <- rf %>% importance_plot(mtcars, mpg)
p2 <- lr %>% importance_plot(mtcars, mpg)
plot_grid(p1, p2, labels = c("Random Forest Feature Importances", "Linear Regression Feature Importances"))
```

### Partial dependence effect plot

To display a partial dependence effect plot of a random forest feature all you need to do is pipe the `rf` object into the `effect_plot` function along with the data set (`mtcars`) and the name of the feature. Here the `purrr` and `cowplot` packages are used to display for effect plots for the four most "important" features (`disp`, `wt`, `hp` and `cyl`)

```{r message=FALSE, warning=FALSE}
library(purrr)

feature_names <- c("wt", "disp", "hp", "cyl")
rf_plots <- map(feature_names, effect_plot, object = rf, new_data = mtcars)
plot_grid(plotlist = rf_plots, labels = "Random Forest Feature Effects")
```

Note that effect of the `disp` variable is reversed in the linear regression model. This is because the random forest captures interactions between the features of the model whereas the linear regression model does not. 

```{r}
lr_plots <- map(feature_names, effect_plot, object = lr, new_data = mtcars)
plot_grid(plotlist = lr_plots, labels = "Linear Regression Feature Effects")
```
